Incentivizing Exploration with Heterogeneous Utilities

### 2017-11-24 paper.tex
addressed comments in the intro section

% \item \textit{Citizen Science}:  \cite{frazier2014incentivizing} mentioned for scientific organizations like Galaxy Zoo, they will guide the enthusiasts to explore the less-explored parts of domain. For each enthusiast, he/she may have different preference towards the location's sight-seeing, weather, distance and safety etc. Thus, as the organization, it needs to incentivize each person differently.

\pfcomment{Banguri, I'm a bit confused about the citizen science application --- let's leave it out of the dissertation, but leave it in the paper.  Can you add some more detail?  For example, with Galaxy Zoo, my understanding is that you are looking at galaxies on a computer screen and so there is no weather.  Maybe you are talking about e-bird?  Can you write something that clarifies this and then we can talk more?
Also, if you can come up with an example of an application with implicit attribute feedback, include it here.}

@@

In this problem context, we study a simple policy that usually exploits, incentivizing agents to pull an arm only when the set of agent utility functions that would pull this arm without incentives has probability below a time-varying threshold.  \pfcomment{Say something about what we show for this policy.}

\pfcomment{Talk about how our regret bounds compare to what our regret bounds would be in a homogenous preference setting, to clarify the following sentences.}
These results suggest that heterogeneous agent preferences reduces but does not eliminate the need to incentive exploration, in relation to single-preference settings.  Essentially, heterogeneity provides a certain amount of exploration for free.

@@

At each time $t$, for each arm $i$, we (the principal) offer a non-negative payment $c_{i,t}\geq 0$ based on previous observations.
We assume that agent $t$ chooses to pull the arm that myopically maximizes the sum of this payment and an estimate of the utility obtained $\theta_t \cdot u_{i,t}$ where $u_{i,t}$ denotes the simple average of $O_s$ over all previous pulls of arm $i$ if it has been pulled at least once, or a default value of $0$ if not.  That is, $u_{i,t} = \sum_{s<t} O_s 1\{A_s = i\} / \sum_{s<t} 1\{A_s = i\}$ if the denominator is strictly positive and $0$ otherwise; and $A_t=\argmax_{i}\{\theta_t\cdot u_{i,t}+c_{i,t}\}$, breaking ties in favor of the arm with the highest incentive.  We use $c_t=c_{A_{t},t}$ to denote the actual incentive payment at time $t$. For simplicity, we assume all arms have been pulled once at time $t=1$ in this paper (we can offer a large payment at the beginning to make this happen). \pfcomment{Bangrui, I assumed that $u(i,t)$ starts from $0$.  Do you want to do this, or do you want to assume that every arm is pulled at least once?  Or do you want to assume that they start from some general starting value?  We could perhaps do the analysis assuming they start from $0$, but then comment that the proofs all carry through if they start from some other value.}

>>>>

We can also apply our models to scientific organizations like eBird \cite{frazier2014incentivizing}. EBird is a website which guides the enthusiasts to explore and report their findings to the bird community. In each report, it contains information such as when, where and how they go birding as well as what kinds of birds they see and hear. As the orginization, EBird needs to incentivize the enthusiasts to explore the less-explored parts of domain. For each enthusiast, he/she may have different preference towards the location's sight-seeing, weather, distance and safety etc. By offering enthusiasts incentivies, eBirds can obtain more reports about the less-explored area and have more information for the bird community.\bccomment{How about this eBird application?}

@@

In this problem context, we study a simple policy that usually exploits, incentivizing agents to pull an arm only when the set of agent utility functions that would pull this arm without incentives has probability below a time-varying threshold. In our paper, we assume all arms are some agents' best arm. Under this assumption, we prove with $O(N^2)$ payment budget, we can bound the cumulative expected regret by $O(N^2+M(\log(T))^2)$ where $M$ is the upper bound of the marginal density for those agents who are indifferent between their best and the second best arm. In the case that $M=0$, which typically happens when the user preference distribution is discrete, we can achieve constant cumulative expected regret $O(N^2)$. The key difference between our problem setting and the homogenous preference setting (or the traditional multi-armed bandits setting) is that we do not need to incentivize the agents to try a suboptimal arm very often since all arms are some agents's best arm. These results suggest that heterogeneous agent preferences reduces but does not eliminate the need to incentive exploration, in relation to single-preference settings. Essentially, heterogeneity provides a certain amount of exploration for free. \bccomment{How about now?}

@@

At each time $t$, for each arm $i$, we (the principal) offer a non-negative payment $c_{i,t}\geq 0$ based on previous observations.
We assume that agent $t$ chooses to pull the arm that myopically maximizes the sum of this payment and an estimate of the utility obtained $\theta_t \cdot u_{i,t}$ where $u_{i,t}$ denotes the simple average of $O_s$ over all previous pulls of arm $i$ if it has been pulled at least once, or a default value of $0$ if not.  That is, $u_{i,t} = \sum_{s<t} O_s 1\{A_s = i\} / \sum_{s<t} 1\{A_s = i\}$ if the denominator is strictly positive and $0$ otherwise; and $A_t=\argmax_{i}\{\theta_t\cdot u_{i,t}+c_{i,t}\}$, breaking ties in favor of the arm with the highest incentive.  We use $c_t=c_{A_{t},t}$ to denote the actual incentive payment at time $t$. For simplicity, we assume all arms have been pulled once at time $t=1$ in this paper, i.e. $u(i,0)=1$ for all $i$. \bccomment{Peter, is it ok that I assume $u(i,0)$ starts with 1?}
